Pillar 1 - Sequential Pattern Mining

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
stop caching manually transactions and sequences

```{r, include = FALSE}
save(
  transactions, sequences,
  d_transcript_cum,
  d_support, n_students,
  file = "Output/Transaction and Sequences.RDATA"
  )
```

```{r, include = FALSE}
rm(

  high_grade, pass_grade, 
  course_all, student_all, n_students,

  d_transactions, d_support, d_transcript_cum,

  make_transaction, transactions, 
  make_sequence, sequences

  )
```

@@

```{r}
load("Output/Transaction and Sequences.RDATA")
```

>>>>

```{r, include = FALSE}
rm(
  high_grade, pass_grade, course_all, student_all, n_students,
  d_transactions, d_support, d_transcript_cum,
  make_transaction, transactions, make_sequence, sequences
  )
```

@@
